\documentclass{article}

\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc}

\title{\textbf{WizardGame}}
\author{
    Dumitru Mițca\\
    Faculty of Automatic Control and Computer Engineering, Iași\\
    dumitru.mitca@student.tuiasi.ro}
\date{2022-2023}

\begin{document}
    \maketitle

    baga niste imagini jmek aici cand arata bine jocul

    \section{Gameplay}
    Aici pun gameplayul

    \section{Plot}

    In the year 1964, Adrian, the Shaman of Neamț, has announced to the magic world that he
    shall destory the Carpathian Mountains and used a powerful spell to steal the magic books of
    every other wizard in Romania. Only Mircea, the Wizard of Brăila, the best fire magician in the
    country, is able to save the Carpathians now. Using the spell he can cast without seeing the
    runes --- fireball --- he shall stop Adrian from his evil plan.

    \section{Characters}
    \begin{itemize}
        \item \textbf{Mircea}, \emph{The Wizard of Brăila} --- the protagonist and player character
        of the game, he wishes to stop Adrian from accomplishing his destructive goal.
        \item \textbf{Adrian}, \emph{The Shaman of Neamț} --- the antagonist, he wishes to
        destroy the Carpathians to avenge the singer Michael Jackson, who had been killed at a concert
        held in the Carphatian Mountains.
        \item \textbf{Matei}, \emph{The Sensei} --- Mircea's mentor, he tragically dies in the tutorial.
        \item \textbf{Mihai} --- Mircea's best friend and a fellow fire magician. He has lost his hand
        in the war of 1959 and is thus unable to help Mircea battle Adrian.
    \end{itemize}

    \section{Mechanics}
    pew pew
\end{document}
